Application-Level Regression Testing Framework using Jenkins

### 2017-06-01 manuscript_ccpe/manuscript.tex
Updated BW acknowledment.

% use section* for acknowledgement
\section*{Acknowledgment}
We thank Gary Rogers at NICS for his help in setting up and testing OTP integration. This material is based upon work performed using computational resources at the National Institute for Computational Sciences (NICS) and the National Center for Supercomputing Applications (NCSA), funded by the National Science Foundation (NSF). NICS is supported by the University of Tennessee and Oak Ridge National Laboratory through the Joint Institute for Computational Sciences\footnote{http://www.jics.tennessee.edu}. A portion of this research used resources of the Oak Ridge Leadership Computing Facility at the Oak Ridge National Laboratory, which is supported by the Office of Science of the U.S. Department of Energy under Contract No. DE-AC05-00OR22725.

>>>>

% use section* for acknowledgement
\section*{Acknowledgment}
This material is based upon work performed using computational resources at the National Institute for Computational Sciences (NICS). NICS is supported by the University of Tennessee and Oak Ridge National Laboratory through the Joint Institute for Computational Sciences\footnote{http://www.jics.tennessee.edu}. This material is part of the Blue Waters sustained-petascale computing project, which is supported by the National Science Foundation (awards OCI-0725070 and ACI-1238993) and the state of Illinois. Blue Waters is a joint effort of the University of Illinois at Urbana-Champaign and its National Center for Supercomputing Applications. A portion of this work used resources of the Oak Ridge Leadership Computing Facility at the Oak Ridge National Laboratory, which is supported by the Office of Science of the U.S. Department of Energy under Contract No. DE-AC05-00OR22725.
